\sysfull

### 2018-08-05 paper/asplos19/intro.tex
revisions to intro (not complete)

%%%%%%%%%%%%%%%%%%%%%% IMPORTANT INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SRAM read/write latency is in the order of 8ns 		 [ Intermittent computation without hardware support of programmer intervention]
% FRAM read/write latency is in the orfer of 60ns/100ns  [Texas Instrument MSP430FR573x DataSheet]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Advances in processor efficiency along with the development of
energy-harvesting systems have created a new category of devices that require
neither a battery nor a tethered power
supply~\cite{prasad_comst_2014,lucia_snapl_2017,soyata_csm_2016}. These
devices operate using ambient energy, such as radio frequency
transmissions~\cite{rf_powered_computing_gollakota_2014},
light~\cite{margolies_infocom_2016,margolies_tosn_2016}, and
vibration~\cite{gorlatova_sigmetrics_2014}. Incorporating compute, storage,
sensing, and communication hardware~\cite{wisp5,moo,capybara}, such devices are a
promising technology for use in the Internet of Things~\cite{ku_cst_2016},
in-body~\cite{nadeau_naturebio_2017} and
on-body~\cite{bandodkar_electroanalysis_2015} medical systems, and
energy-harvesting nano-satellites~\cite{kicksat,capybara}.
%
Energy-harvesting devices create unique challenges because they operate {\em
intermittently} when energy is
available~\cite{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device
buffers energy in a small storage capacitor~\cite{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a
threshold amount of energy has accumulated. Harvestable energy sources are low-power (e.g., \si{\nano\watt}\ to \si{\micro\watt}) compared to a platform's operating
power level (hundreds of \si{\micro\watt}\ to \si{\milli\watt}). A device operates briefly until it depletes its buffered energy, after which, it shuts
down and recharges to operate again later---corresponding to the {\em intermittent execution model}~\cite{dino,lucia_snapl_2017} composed of
operation-power failure-restart cycles. 
The recharge and discharge intervals---which correspond to the device's inactive and active time---vary with the energy buffering capacitor~\cite{capybara} \note{not only, though} and some devices fail and restart operating $\approx$10 to
$\approx$100 times per second~\cite{tan_infocom_2016,mementos,nvp}.
%
%\textbf{Data Consistency in Intermittent Computing.}

@@

%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-v3.pdf}
    \caption{\note{small static task subplot and large static task subplot can be re-arranged to fit next to each other, so we end up with two layers plot} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
\note{Why no indent?}
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following dilemma: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead.

\noindent\textbf{Challenges and Contributions.}
\note{Why no indent?}
This paper introduces \sys, a new task-based system that employs \emph{adaptive task size execution by task coalescing/splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks (Fig.~\ref{fig:coalesce}, top) or splits them (Fig.~\ref{fig:coalesce},bottom) based on the estimated energy availability without demanding any hardware support. \note{\textbf{To the best of our knowledge, \sys is the only task-based system that guarantees task termination and ....(something related with Coalescing...)  }}

>>>>

Advances in processor efficiency along with the development of energy-harvesting systems have created a new category of devices that require neither a battery nor a tethered power supply~\cite{prasad_comst_2014,lucia_snapl_2017,soyata_csm_2016}. These devices operate using ambient energy, such as radio frequency transmissions~\cite{rf_powered_computing_gollakota_2014},
light~\cite{margolies_infocom_2016,margolies_tosn_2016}, and vibration~\cite{gorlatova_sigmetrics_2014}. Incorporating compute, storage, sensing, and communication hardware~\cite{wisp5,moo,capybara}, such devices are a promising technology for use in the Internet of Things~\cite{ku_cst_2016}, in-body~\cite{nadeau_naturebio_2017} and on-body~\cite{bandodkar_electroanalysis_2015} medical systems, and energy-harvesting nano-satellites~\cite{kicksat,capybara}. Energy-harvesting devices create unique challenges because they operate {\em intermittently} when energy is available~\cite{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device buffers energy in a small storage capacitor~\cite{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a threshold amount of energy has accumulated. Harvestable energy sources are low-power (e.g., \si{\nano\watt}\ to \si{\micro\watt}) compared to a platform's operating power level (hundreds of \si{\micro\watt}\ to \si{\milli\watt}). A device operates briefly until it depletes its buffered energy, after which, it shuts down and recharges to operate again later---corresponding to the {\em intermittent execution model}~\cite{dino,lucia_snapl_2017} composed of operation-power failure-restart cycles. The recharge and discharge intervals---which correspond to the device's inactive and active time---vary depending on the underlying hardware, such as the size of the energy buffering capacitor~\cite{capybara}, and some devices discharge and restart $\approx$10 to $\approx$100 times per second~\cite{tan_infocom_2016,mementos,nvp}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-v3.pdf}
    \caption{\note{small static task subplot and large static task subplot can be re-arranged to fit next to each other, so we end up with two layers plot} \note{Add distinction: top---legacy task-based system; bottom---Coala} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\textbf{Crucial Drawback of Static Task Decomposition.} Task-based programming and execution models require a programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow. Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime. A programmer may thus create very large tasks in an attempt to reduce task transitions overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk, existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following dilemma: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead.

\textbf{Challenges and Contributions.} This paper introduces \sys, a new task-based system that employs \emph{adaptive task size execution by task coalescing/splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks (Fig.~\ref{fig:coalesce}, top) or splits them (Fig.~\ref{fig:coalesce},bottom) based on the estimated energy availability without demanding any hardware support. \note{\textbf{To the best of our knowledge, \sys is the only task-based system that guarantees task termination and ....(something related with Coalescing...)  }}
